### 2023-04-15 tex/article.tex
Remove hyphen shorthands

\begin{figure}
  \centering
  \includegraphics[width=12cm]{article/zone_separation.pdf}
  \caption[Delimitation of biomes]{
    Delimitation of the three biomes in the Gulf stream extension region: the Permanent Subtropical Biome~(PSB, south of the dashed line at~\latlon{32N}), the Seasonal Subtropical Biome~(SSB, between \latlon{32N} and the meandering Gulf stream northern wall on that day marked with the black contour), and the Subpolar Biome~(PB, north of the Gulf stream northern wall).
    (a)~SST and (b)~\as{chl} snapshots on the 22 April 2007 (with data masked by clouds in white), (c)~SST and (d)~\as{chl}  distribution within each biome for the same day (PB:\@ blue, SSB:\@ yellow, PSB:\@ red).
    The black line in~(c) shows the SST threshold value detected to delimit the Gulf Stream northern wall~(see methods section).
    The x"-axis of the distributions correspond to the x-axis scale of the corresponding color bars.
    The red line follows the~\qty{1500}{m} isobath.
    Data on the continental shelf~(\qty{<1500}{\m}) is not considered here and have been masked.
  }%
  \label{fig:zone-separation}
\end{figure}

@@

The strength of the local excess in \as{chl} over fronts also depends on latitude.
In the permanent subtropical biome (\nref{fig:latbands-s}), the excess is only detectable north of~\latlon{25N} and remains modest (\(\am{exces} < \pct{10}\)); it reaches its maximum of~\pct{10} at the beginning and end of the production season.
In the seasonal subtropical biome (\nref{fig:latbands-i}), the excess is also small in the southern part of the biome (south of~\latlon{35N}) but strongly increases further north (between \latlon{35N} and~\latlon{45N}) and decreases again going even further North (between \latlon{40N} and~\latlon{45N}).
moreover, in this biome, the increase is stronger in summer (July"-August) compared to winter (December"-January).
Finally in the subpolar biome, the magnitude of the local excess diminishes going northward.
It tends to be stronger during winter and during the bloom, and weaker in summer.
In fact in summer, the differences are hardly discernible when averaged over the entire biome (\nref{fig:ts-climato}c), but there is an excess \as{chl} in the southern part of the biome (\latlon{<45N}), and a slightly deficit in the northern part of the biome (\latlon{>45N})~(\nref{fig:latbands-n}).

@@

The level~4 SST product used in this study has the advantage to be readily available on download platforms (here \as{cmems}) at a reasonably high spatial resolution~(\qty{4}{\km}), avoiding the need to regrid as was done in \textcite{liu_2016} who used~\qty{1}{\km} resolution \abbrv{L2} \as{modis}"-Aqua data.
It also has an excellent spatial coverage (\nref{fig:zone-separation}) as it includes merged data from several sensors, but there is a trade-off between coverage and resolution.
We have performed initial tests to investigate the differences in using 1km and 4km resolution SST data, which convinced us that the use of~\qty{4}{\km} resolution data was appropriate (not shown), particularly since the heterogeneity index HI is computed here over boxes of~\qtyproduct{30 x 30}{\km}.
Nevertheless a more in-depth study of the sensitivity of our results to the resolution of the satellite products could be carried out in the future.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=12cm]{article/zone_separation.pdf}
  \caption[Delimitation of biomes]{
    Delimitation of the three biomes in the Gulf stream extension region: the Permanent Subtropical Biome~(PSB, south of the dashed line at~\latlon{32N}), the Seasonal Subtropical Biome~(SSB, between \latlon{32N} and the meandering Gulf stream northern wall on that day marked with the black contour), and the Subpolar Biome~(PB, north of the Gulf stream northern wall).
    (a)~SST and (b)~\as{chl} snapshots on the 22 April 2007 (with data masked by clouds in white), (c)~SST and (d)~\as{chl}  distribution within each biome for the same day (PB:\@ blue, SSB:\@ yellow, PSB:\@ red).
    The black line in~(c) shows the SST threshold value detected to delimit the Gulf Stream northern wall~(see methods section).
    The x"~axis of the distributions correspond to the x"~axis scale of the corresponding color bars.
    The red line follows the~\qty{1500}{m} isobath.
    Data on the continental shelf~(\qty{<1500}{\m}) is not considered here and have been masked.
  }%
  \label{fig:zone-separation}
\end{figure}

@@

The strength of the local excess in \as{chl} over fronts also depends on latitude.
In the permanent subtropical biome (\nref{fig:latbands-s}), the excess is only detectable north of~\latlon{25N} and remains modest (\(\am{exces} < \pct{10}\)); it reaches its maximum of~\pct{10} at the beginning and end of the production season.
In the seasonal subtropical biome (\nref{fig:latbands-i}), the excess is also small in the southern part of the biome (south of~\latlon{35N}) but strongly increases further north (between \latlon{35N} and~\latlon{45N}) and decreases again going even further North (between \latlon{40N} and~\latlon{45N}).
moreover, in this biome, the increase is stronger in summer (July-August) compared to winter (December-January).
Finally in the subpolar biome, the magnitude of the local excess diminishes going northward.
It tends to be stronger during winter and during the bloom, and weaker in summer.
In fact in summer, the differences are hardly discernible when averaged over the entire biome (\nref{fig:ts-climato}c), but there is an excess \as{chl} in the southern part of the biome (\latlon{<45N}), and a slightly deficit in the northern part of the biome (\latlon{>45N})~(\nref{fig:latbands-n}).

@@

The level~4 SST product used in this study has the advantage to be readily available on download platforms (here \as{cmems}) at a reasonably high spatial resolution~(\qty{4}{\km}), avoiding the need to regrid as was done in \textcite{liu_2016} who used~\qty{1}{\km} resolution \abbrv{L2} \as{modis}-Aqua data.
It also has an excellent spatial coverage (\nref{fig:zone-separation}) as it includes merged data from several sensors, but there is a trade-off between coverage and resolution.
We have performed initial tests to investigate the differences in using 1km and 4km resolution SST data, which convinced us that the use of~\qty{4}{\km} resolution data was appropriate (not shown), particularly since the heterogeneity index HI is computed here over boxes of~\qtyproduct{30 x 30}{\km}.
Nevertheless a more in-depth study of the sensitivity of our results to the resolution of the satellite products could be carried out in the future.
